%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv-a4} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{john}{gillott}{programmer} % Your name and current job title/field

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Manchester
UK
~
jsgtwenty at gmail.com
\href{https://www.johngillott.com/}{johngillott.com}
\href{https://github.com/johngillott}{github.com/johngillott}
\href{https://www.linkedin.com/in/johngillott/}{linkedin.com/in/johngillott}
\href{https://twitter.com/jsgtwenty}{twitter.com/jsgtwenty}
\section{languages}
English
\section{programming}
Adept:
Go, SQL, TypeScript
~
Proficient:
Docker, Kubernetes, Git, HTML, CSS, Bash
~
Learning:
Rust
~
Forgotten:
Java, C++, Python
\end{aside}

\section{profile}

A highly passionate software engineer specialized in Go (Golang) and TypeScript, with experience in writing low-latency, highly available and scalable microservices for staffing and finance domain, and sports betting industry.
I enjoy the dynamic of working in a progressive environment and knowing that my work directly affects the direction and success of the business. I have experience of working autonomously; however I recognize the greater value of
both teamwork and collaboration.

\section{employment}
\begin{entrylist}

\entry
{2019 ...}
{bet365}
{Manchester, UK}
{\emph{Software Engineer} \\
Since May 2019, I am a member of the Sports Development team responsible for delivery of real time content across desktop and mobile client products, to the processing and settlement of transactions driven from that content.
\begin{itemize}
\item Co-authored a high performance XML encoder package in Go.
\item Developed reusable UI components for Web and Mobile using TDD practices, written in a custom TypeScript framework.
\item Migrated monolithic services written in C\# into low-latency, highly available and scalable Go microservices.
\end{itemize}
\small{\textit{Golang, TypeScript, Docker, ELK Stack}}
}

\entry
{2017 -- 2019}
{GRI UK}
{Knutsford, UK}
{\emph{Graduate Software Engineer, Software Engineer} \\
Since March 2017, I was in the team that developed services for the fulfillment and invoicing of workforce for both public and private sectors through the UK. Working as a part of
a small team on B2B software using Angular and Go.
\begin{itemize}
\item Developed scalable, RESTful microservices and internal packages in Go with support for JSON Web Tokens, AWS services.
\item Refactored and redesigned an algorithm for processing candidates' work history to calculate candidates' Permanent Equivalent Rate status, with respect to Agency Worker Regulations, for tens of thousands of
candidates on a weekly basis.
\item Influenced the system design and contributed to the technical architecture of core systems including migrating databases from Amazon Relational Database Service to Amazon Aurora, and containerized microservices to Functions as a Service in AWS.
\end{itemize}
\small{\textit{Golang, Angular, AWS, Docker, Lambda, MySQL, Python, Jenkins, ELK Stack}}
}

\end{entrylist}

\begin{entrylist}

\entry
{2016 -- 2017}
{University of Leicester, Department of Mathematics}
{Leicester, UK}
{\emph{Software Engineer (part time)} \\
Responsible for eliciting and managing client requirements to design, development and delivery of a trading simulator platform for undergraduate actuarial science students.
\begin{itemize}
\item Sourced and analyzed client requirements to create technical deliverables.
\item Provided Java EE, Spring MVC, and Hibernate ORM expertize to team members.
\item Worked in a small team with a project manager and other software engineers to deliver features using Agile practices.
\end{itemize}
\small{\textit{Java EE, Spring MVC, Hibernate ORM, MySQL, JavaScript/ES6, MySQL, jQuery}}
}

\end{entrylist}

\section{education}

\begin{entrylist}

\entry
{2011 -- 2016}
{MComp {\normalfont Computer Science}, 2:1}
{University of Leicester}
{
    \textit{Final year project:} An android application to detect and automatically skip over advertisements in digital audio media such as podcasts.
    Included courses on: Advanced C++ Programming; Service-Oriented Architectures; Advanced Web Technologies; Internet and Cloud Computing.
    \\\textit{Third year project:} A system to record the attendance of university students using smart card technology to perform identity verification, and a web portal for department staff members to manage smart cards and monitor class attendance.
    Included courses on: Databases and Web Applications; Operating Systems, Networks, and Distributed Systems; Cryptography and Internet Security.
}

\end{entrylist}

\section{recommendations}

\begin{entrylist}

\entry
{May 2019}
{Ryan Gough}
{Head of Engineering at GRI UK, Oct 2017 ...}
{
    John is an excellent software developer who I was lucky enough to work with for just under 2 years at GRI. He lead the development effort on some complex pieces of work and did a great job. He helped push through improvements to working practices and was generally a fantastic team member. John would be a great asset for any software development team.
}

\entry
{Jan 2019}
{Justin Taylor}
{Head of Engineering at GRI UK, Sep 2015 -- Oct 2017}
{
    I hired John through our graduate programme, through which he showed immediate promise and his infectious enthusiasm. He is diligent, genial and as effective on a solo project as he is in an agile team. I am proud that he chose our company as his first opportunity to excel in a commercial environment and firmly believe that he'd be an asset to any software engineering team.
}

\end{entrylist}

\section{interests}

\textbf{personal:} Running, Scuba Diving, and Video Games \\
\textbf{professional:} Static Analysis Tools, Community-driven Developer Meetups, and Go

\end{document}